Balsa: A Compact Line Notation Based on SMILES

### 2022-07-09 manuscript.tex
Removes paragraph and figure for fastener. Closes #23

Regardless of the form taken by the input data structure, it must be traversable in \textit{depth-first} order. A depth-first traversal operates over a set of nodes bound by a set of connectivity relationships, which are typically edges. Traversal proceeds by successively replacing each node as the center of focus, or root. Each new root is chosen from the untraversed neighbors of the current root. Eventually all nodes are processed, ending the traversal.

@@

The presence of branches within an input data structure is encoded via the \ttt{<branch>} non-terminal. A useful tool for this purpose is a \ttt{stack}. A stack is a data structure that allows items to be added individually and removed (\enquote{popped}) in the reverse order of addition. A writer begins by pushing the current branch onto the stack and extending it. When a new branch is encountered, it is pushed to the stack and extended. When the branch terminates, the current branch is popped and its contents are appended to the stack's new top item.

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{stack-for-writer.pdf}
    \caption{Stack for writing strings. Traversal of the root atom (C) creates a new entry. Encountering the start of a branch (N, S) creates a new entry preceded by an open parenthesis symbol (\ttt{(}). Extending a branch writes to the top stack item (I, F, O). Closing a branch pops the top item then concatenates it, together with a close parenthesis symbol (\ttt{)}), to the new top item.}
    \label{fig:branch-stack}
\end{figure}

@@

Transformation of tree to graph can be aided by a \textit{fastener} (Figure~\ref{fig:fastener}). A fastener is a key/value store whose keys are bridge indexes and whose values are a tuple composed of: (1) the identifier of the last atom added to the graph; and (2) the bridge bond attributes \ttt{order}, \ttt{elided}, and \ttt{direction}. Odd insertions (first, third, etc.) associate the bridge index with the tuple and return \ttt{None}. Even insertions (second, fourth, etc.) remove the previously-associated tuple and return it. A fastener is paired with a depth-first traversal of the tree to be transformed. On encountering a bridge, an insertion is made. If the return value is a tuple, it is used together with the current gap bond attributes and atom identifier to create a bond and place it within the molecular graph.

\begin{figure}
    \centering
    \includegraphics{filler}
    \caption{Fastener. Use of a fastener with the depth-first traversal of a molecular tree aids transformation to a molecular graph.}
    \label{fig:fastener}
\end{figure}

>>>>

Regardless of the form taken by the input data structure, it must be traversable in \textit{depth-first} order (Figure~\ref{fig:depth-first-traversal}). A depth-first traversal operates over a set of nodes bound by a set of connectivity relationships, which are typically edges. Traversal proceeds by successively replacing each node as the center of focus, or root. Each new root is chosen from the untraversed neighbors of the current root. Eventually all nodes are processed, ending the traversal.

@@

The presence of branches within an input data structure is encoded via the \ttt{<branch>} non-terminal. A useful tool for this purpose is a \ttt{stack} (Figure~\ref{fig:stack-for-writer}). A stack is a data structure that allows items to be added individually and removed (\enquote{popped}) in the reverse order of addition. A writer begins by pushing the current branch onto the stack and extending it. When a new branch is encountered, it is pushed to the stack and extended. When the branch terminates, the current branch is popped and its contents are appended to the stack's new top item.

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{stack-for-writer.pdf}
    \caption{Stack for writing strings. Traversal of the root atom (C) creates a new entry. Encountering the start of a branch (N, S) creates a new entry preceded by an open parenthesis symbol (\ttt{(}). Extending a branch writes to the top stack item (I, F, O). Closing a branch pops the top item then concatenates it, together with a close parenthesis symbol (\ttt{)}), to the new top item.}
    \label{fig:stack-for-writer}
\end{figure}

@@
